\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-23 paper.tex
3.3 revised

For an s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth to the demanded bandwidth under network scenario $\mathbf{z}$, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z.
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}. 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle a linear programming problem.

Let $B_d^{\mathbf{z}}$ denote the lower bound of $R_{dk}^{\mathbf{z}}$ over all s-d pairs, i.e.,
\begin{eqnarray} \label{B2}
B_d^{\mathbf{z}} \le R_{dk}^{\mathbf{z}}, \quad  \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z
\end{eqnarray}
%It is obvious  $B_d^{\mathbf{z}} \le 1$ and $B_d^{\mathbf{z}}=1$ presents scenario $\mathbf{z}$ is qualified, therefore, 
and define $B_d^{\mathbf{z}}\times p_{\mathbf{z}}$ as the potential achieved availability  
under network scenario  $\mathbf{z}$, which is set to be no smaller than the availability target, i.e., 
\begin{eqnarray} \label{Achieved}
\sum_{\mathbf{z}\in Z}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{d},  \quad {\forall d \in \hat{D}}
\end{eqnarray}

@@

Solving this LP problem directly is possible, but as it considers every possible network scenario, 
the complexity will increase exponentially with the network size.
%For example, we consider a small inter-DC WAN which contains 3 links and  5 events.
%Each link has $2^5=32$ states and the network includes $32^3=32768$ states in total. 
%In reality, network scale is much larger and  the states volume will increase exponentially.
For instance, the B4 topology \cite{B4} has 12 nodes and 38 links,
so there are totally $2^{38}$ network failure scenarios (when only link failures considered).
%The explosive network scenarios make it impossible to solve $\mathsf{BATE}$ problem.
Therefore, an important question is \textit{how to effectively reduce the problem size without 
affecting the result significantly}. 
TEAVAR \cite{Teavar} prunes a scenario if its probability is smaller than a threshold. However, such a threshold is difficult to choose, and it still has to enumerate all 
possible scenarios. Instead, we use a much faster pruning method, 
where at most two concurrent link failures will be considered in our network scenarios, 
and all the remaining scenarios will be converted into one special \textit{unqualified} scenario. 
In this way, the set of scenarios $Z$ and the corresponding $\{p_\mathbf{z}\}$ can be efficiently computed.

>>>>

For an s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth under network scenario $\mathbf{z}$ to the demanded bandwidth, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z.
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}, i.e., 
$\mathbf{z} \propto <d, \{f_d^t\}> \Leftrightarrow R_{dk}^{\mathbf{z}} \ge 1$. 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle a linear programming problem.

Let $B_d^{\mathbf{z}}$ denote the lower bound of $R_{dk}^{\mathbf{z}}$ over all s-d pairs, i.e.,
\begin{eqnarray} \label{B2}
B_d^{\mathbf{z}} \le R_{dk}^{\mathbf{z}}, \quad  \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z
\end{eqnarray}
%It is obvious  $B_d^{\mathbf{z}} \le 1$ and $B_d^{\mathbf{z}}=1$ presents scenario $\mathbf{z}$ is qualified, therefore, 
and use $B_d^{\mathbf{z}}\times p_{\mathbf{z}}$ to roughtly represent the availability that can be achieved   
under network scenario  $\mathbf{z}$, which is set to be no smaller than the availability target, i.e., 
\begin{eqnarray} \label{Achieved}
\sum_{\mathbf{z}\in Z}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{d},  \quad {\forall d \in \hat{D}}
\end{eqnarray}

@@

Solving this LP problem directly is possible, but as it considers every possible network scenario, 
the complexity will increase exponentially with the network size.
%For example, we consider a small inter-DC WAN which contains 3 links and  5 events.
%Each link has $2^5=32$ states and the network includes $32^3=32768$ states in total. 
%In reality, network scale is much larger and  the states volume will increase exponentially.
For instance, the B4 topology \cite{B4} has 12 nodes and 38 links,
so there are totally $2^{38}$ network failure scenarios (when only link failures considered).
%The explosive network scenarios make it impossible to solve $\mathsf{BATE}$ problem.
Therefore, an important question is \textit{how to effectively reduce the problem size without 
affecting the result significantly}. 
TEAVAR \cite{Teavar} prunes a scenario if its probability is smaller than a threshold. However, such a threshold is difficult to choose, and an enumeration of all 
possible scenarios is still needed. Instead, we use a much faster pruning method, 
where at most two concurrent link failures will be considered, 
and all the remaining scenarios will be aggregated into one special \textit{unqualified} scenario. 
In this way, the set of scenarios $Z$ and the corresponding probabilities $\{p_\mathbf{z}\}$ can be efficiently computed.
